[barman]
; Generic barman buy multipliers.
; He runs a bar, not an arms store. Food, drink, smokes — that's his economy.
; Mutant meat is his best buy: the cook needs a steady supply.
; Zone items (artifacts) are accepted — barmans fence these as a side business.
; Everything weapon or gear related is simply not his problem.
; Normalized to 1.0 max. General trader_discount applied separately.

; --- WEAPONS ---
; Not his business. At all.
wpn_pistol_rus_low
wpn_pistol_rus_high
wpn_pistol_nato_low
wpn_pistol_nato_high
wpn_rifle_rus_low
wpn_rifle_rus_mid
wpn_rifle_rus_high
wpn_rifle_nato_low
wpn_rifle_nato_mid
wpn_rifle_nato_high
wpn_sniper_rus
wpn_sniper_nato
wpn_shotgun_rus_low
wpn_shotgun_rus_high
wpn_shotgun_nato_low
wpn_shotgun_nato_high
wpn_lmg_rus
wpn_lmg_nato
wpn_addons
wpn_melee
wpn_explosive

; --- AMMO ---
ammo_rus_common
ammo_rus_mid
ammo_rus_rare
ammo_nato_common
ammo_nato_mid
ammo_nato_rare
ammo_degraded

; --- OUTFITS & HEADGEAR ---
outfit_novice
outfit_stalker
outfit_armored
outfit_exo
outfit_scientific
headgear_basic
headgear_combat

; --- EQUIPMENT ---
backpacks

; --- REPAIR ---
repair_kits_weapon
repair_kits_outfit
parts_weapon
parts_outfit
parts_misc

; --- DEVICES ---
devices_basic
devices_advanced

; --- TOOLS ---
tools

; --- PATCHES ---
patches

; =============================================================================
; WHAT HE ACTUALLY BUYS
; =============================================================================

; --- FOOD ---
; Cooked mutant meat: the cook's primary ingredient — best buy rate
food_zone             = 1.0, 0.85
; Packaged and preserved food: restocking the pantry
food_packaged           = 0.80, 0.65

; --- DRINKS ---
; Basic drinks: water and non-alcoholic — always needed
drink_basic             = 0.85, 0.70
; Alcohol: the bar's core product — buys well to restock
drink_alcohol           = 1.0, 0.85

; --- DRUGS & SMOKES ---
; Cigarettes: bar staple, fast turnover
cigs                    = 0.90, 0.75
; Basic drugs: bandages, glucose — small first aid stock
drug_basic              = 0.55, 0.40
; Military drugs: not his market
drug_military           = 0.20, 0.12
; Chemical drugs: he's not a dealer, takes them reluctantly
drug_chem               = 0.35, 0.25

; --- ZONE ITEMS ---
; Artifacts: barmans fence these — moderate but real demand
artefacts               = 0.70, 0.55
; Mutant parts: the cook uses some of these, claws and bones less so
mutant_parts            = 0.75, 0.60

; --- CAMPING & FUELS ---
; Camping gear: sells to stalkers passing through
camping                 = 0.55, 0.40
; Fuels: the kitchen burns through kerosene and gas
fuels                   = 0.80, 0.65

; --- TRASH ---
trash                   = 0.10, 0.05
