#include "presets\trade_discounts.ltx"
#include "presets\trade_presets.ltx"

;EDITED GROUNDED TRADER OVERHAUL

[trader]
buy_condition = trade_generic_buy 
sell_condition = trade_generic_sell
buy_supplies = {=drugkit_task_done()} supplies_2, supplies_1
buy_item_condition_factor = 0.40
buy_item_exponent = 2.25
sell_item_exponent = 0.7

sell_item_min_condition = 0.3
sell_item_max_condition = 0.98

discounts = discount_medic

[trade_generic_buy]:medic
itm_pda_common                           ;NO TRADE
itm_pda_rare                             ;NO TRADE
itm_pda_uncommon                         ;NO TRADE
pri_a25_explosive_charge_item            ;NO TRADE

[trade_generic_sell]:medic
itm_drugkit				= 2.0, 2.0

[supplies_1]:common_stock
; The camp medic's basic stock. What they can keep reliably supplied.
; Not everything is always available — field medicine is an imperfect science.
; No heavy drugs until the medic knows who they're dealing with.

; --- WOUND CARE ---
bandage                 = 5, 0.88
jgut                    = 3, 0.75
tetanus                 = 2, 0.66

; --- MEDKITS ---
medkit                  = 3, 0.75
medkit_ai1              = 2, 0.60

; --- ANTIBIOTICS & ANTIRAD ---
antibio_chlor           = 3, 0.75
antibio_sulfad          = 2, 0.66
antirad_kalium          = 3, 0.75
antirad_cystamine       = 2, 0.66
antiemetic              = 2, 0.60
akvatab                 = 3, 0.75

; --- BLOOD & RECOVERY ---
glucose                 = 3, 0.75
glucose_s               = 2, 0.66
protein                 = 2, 0.60

; --- LIGHT PAINKILLERS & BOOSTERS ---
yadylin                 = 2, 0.66
analgetic               = 2, 0.66
caffeine                = 2, 0.60
drug_sleepingpills      = 1, 0.50

; --- BASIC PHARMACEUTICALS ---
drug_booster            = 1, 0.50
drug_antidot            = 1, 0.50
drug_coagulant          = 1, 0.44


[supplies_2]:supplies_1
; The medic knows you now. The back cabinet opens.
; Serious trauma care, stimpacks, surgical-grade drugs.
; Higher quantities across the board — a trusted medic keeps deeper stock.

; --- WOUND CARE UPGRADE ---
bandage                 = 8, 1
jgut                    = 5, 0.88
rebirth                 = 2, 0.66

; --- MEDKITS UPGRADE ---
medkit                  = 5, 0.88
medkit_ai1              = 4, 0.88
medkit_ai2              = 3, 0.75
medkit_ai3              = 2, 0.55
medkit_army             = 3, 0.75
medkit_scientic         = 1, 0.44
survival_kit            = 1, 0.33

; --- STIMPACKS ---
stimpack                = 3, 0.75
stimpack_army           = 2, 0.60
stimpack_scientic       = 1, 0.40

; --- ANTIRAD UPGRADE ---
antirad                 = 3, 0.75
drug_radioprotector     = 2, 0.60
drug_anabiotic          = 1, 0.44

; --- HEAVY PHARMACEUTICALS ---
; Morphine: legitimate surgical painkiller — available to trusted patients
morphine                = 2, 0.60
salicidic_acid          = 3, 0.75
adrenalin               = 2, 0.60
drug_psy_blockade       = 2, 0.55
drug_booster            = 3, 0.75
drug_antidot            = 3, 0.75
drug_coagulant          = 3, 0.75
drug_sleepingpills      = 2, 0.60
